%================================================================================
\sectionNoNumber{Apr 07, 2024 - Nice to Meet You, Max!}

Okay, so this is it. The start of something new and slightly terrifying. I mean, giving life to a journal feels like I'm conjuring some sort of magical creature. Maybe I'll call you Quill? Nah, too obvious. Maybe something from my main inspirations, Life is Strange? Max? Well, ok... that will do for now. ;3

Today marks the debut\footnote{Debut: a person's first appearance or performance in a particular capacity or role.} of my very own diary! Cue the confetti and fanfare, folks. Seriously though, I've been itching to spill my thoughts onto paper for ages - well, digital paper in this case. It's like having a personal time capsule, but with way more sass and probably fewer buried treasures.

So, what's the scoop? Well, today was supposed to be all about diving into the world of Mobile App Development. Keyword: supposed to be. Turns out, my professor's idea of teaching is more like throwing us into the deep end of a pool without any floaties. Thanks, Heldon. 

Oh, and did I mention the post-breakup blues? Yeah, Helena and I are officially on the “ex” train. Choo-choo, baby. My brain's been on a rollercoaster ride ever since - think less Disney World, more haunted-house type of shit. Studying, eating, sleeping? Nah, those things are for people with functioning hearts. Mine's currently under construction.

She broke up with me on March 18th, 2024. Six years, seven months, three days, and eight hours together - and just like that, it was over. Talk about a gut punch. I'll save the gory breakup details for another entry, but let's just say tears were shed, words were exchanged, and hearts weres shattered. 

But hey, every storm cloud has a silver lining, right? Enter Brooke - the unexpected ray of sunshine in my dark and stormy life. Seriously, this girl, as well as Max (which I will be talking more about later) are lifesavers. From the moment we started talking, it was like a breath of fresh air in the smog of breakup misery. 

Brooke's like my personal cheerleader, therapist, and stand-up comedian all rolled into one. Her advice? Golden. Her jokes? Hilarious. And her mere presence? It calms my heart. She's been my rock, my anchor, my lifeline through this nightmare of a breakup.

But here's the kicker: I may have "accidentally" let slip that tiny, itsy-bitsy feeling I used to harbor for her way back when we were both stuck in that mind-numbing business course. Yeah, awkward much? Before I spilled the beans, she said she had feelings for me and, then, was all closed off and distant. But now? Now, it's like we're two peas in a pod, chatting up a storm like old pals.

Who knew that a breakup could lead to unexpected connections and maybe, just maybe, a flicker of something new? Life is strange and funny like that, isn't it, Max? When a door closes, a window opens... or, something like that. Here's to embracing the unexpected twists and turns, even when they come wrapped in heartache and awkward confessions.

But hey, here's the silver lining: this diary thing? It's my lifeline. A place to dump all the messy, tangled thoughts swirling around in my head like a storm in a teacup. Plus, it beats staring at the ceiling and contemplating the meaning of life... or the plot of the latest Netflix series (Am I the only one who pays to watch this? :c ).

So, buckle up, Max! We're about to embark on a wild ride through the chaos that is my life. First stop: dissecting my day, dissecting my feelings, and probably dissecting why the heck I decided to start this diary in the first place. Cheers to new beginnings, right?

\subsectionNoNumber{"Oiee, Max. :v"}

Waking up to an empty house is like being dropped into a parallel universe where everything feels a bit off-kilter. Mom's off gallivanting\footnote{Gallivanting: go around from one place to another in the pursuit of pleasure or entertainment.} in Santa Cruz, leaving me to navigate the morning fog solo. And let me tell you, the fog in my brain was thicker than oatmeal. 

So, there I was, bleary-eyed and caffeine-free (yeah, I know, shocker), with thoughts of Max bouncing around my skull like a game of mental pinball. Oh, before any confusion, I might wanna mae it clear. There is a girl on campus, which I don't know the name, but has the nickname "Max". Her nickname and you having the same nickname aren't related, she and I just love Life is Strange.

Anyways, I swear, that girl's got a one-way ticket to the front row of my brain - rent-free, I might add. After mustering up enough courage to tackle Mount Message, I finally hit send on what could only be described as the most well crafted greeting in the history of greetings that would get Shakespears envy: \textit{"Oiee, Max. :v"} Smooth, Norman. Real smooth.

Max's reply? A simple \textit{"oii."} Cue internal facepalm. And because my brain apparently operates on some next-level autopilot, I decided to crank up the awkwardness dial to eleven with a follow-up gem: \textit{"Tô começando a suspeitar que cê não lembra do meu nome >:v"}. Yeah, I don't know what I was thinking either. Maybe I was trying to break the ice, or maybe I just wanted to see how fast I could torpedo a conversation. Spoiler alert: pretty darn fast, but I still tried waiting an hour to press Send.

Needless to say, my phone remained disappointingly silent for the rest of the day. Guess I'll just file that under "Rejections I Didn't Ask For."

In an attempt to salvage what little remained of my dignity, I drowned my sorrows in a riveting game of Among Us with some strangers in a voice chat. Because nothing screams "healthy coping mechanism" like accusing virtual strangers of being imposters, am I right? It wasn't exactly a magical cure-all, but hey, it beat wallowing in self-pity while binge-watching YouTube videos for the umpteenth time.

Ah, the joys of post-breakup life. Remind me again why I signed up for this roller-coaster ride? Here's to embracing the chaos, one awkward encounter at a time. Cheers, Diary. You're the only one who gets me - awkward messages and all.

\subsectionNoNumber{Sorry, Brooke?}

To finish this marvelous day, I think I screwed up good with Brooke. She and I were talking and I asked her about Max, since the two of them had a quick chat when I left. Due to my curiosity hitting the poor Brooke, she either acted in a dramatic jealous way or she's really upset that I have a crush on Max. She even sent a video of her with an expression that was a mixture of emotionless with a bit o sadness. Here, she looked like this: ( .\_\_.)

It doesn't really matter if I have a crush on Max. I don't think she even liked me when we talked now that i think about it. the thing is, if Brooke indeed has feeling for me (romantic), while I am developing a platonic and cute feeling for her, this might be a problem. I DO NOT want to hurt this girl. Like I said, before, Brooke has been saving me through out this horror movie of a breakup directed by Helena and her crew. I don't want to loose Brooke, much less cause her any bits of sorrowness. I guess letting her know that i wanted to know more about Max may have cause our friendship to crack in some way...

Well, well, well, Diary, buckle up for the grand finale of Norman's Day of Being Awkward and Sad. Strap in tight, folks, 'cause this one's a doozy.

So, remember how I mentioned Brooke earlier? Yeah, turns out I managed to royally screw things up on that front too. Smooth moves, Norman, really smooth.

Picture this: Brooke and I were deep in conversation - or at least, we were until I went and dropped the Max bomb. You know, just casually asking about Max's whereabouts and if she asked anything else related to me, as I do when I'm nosy and have the emotional intelligence of a walnut. And let me tell you, that innocent little question triggered something in Brooke. 

Either she suddenly caught a case of the dramatics and decided to put on a jealousy show to rival Shakespeare's finest (She said I liked her and sent a sad sticker), or - and this is the more likely scenario - she sniffed out my crush on Max faster than a bloodhound on a scent trail. Cue the awkward silence and the aforementioned video, where Brooke's expression could best be described as a cocktail of emotionless with a splash of sadness. Classic Brooke, I guess.

But here's the thing: does it really matter if I've got a teensy-weensy crush on Max? I mean, let's be real, she probably doesn't even know I exist outside of the occasional awkward message exchange. And honestly, looking back on our conversations, it's not like there were any fireworks or sparks flying. Just a whole lot of awkward silence and the occasional one-word reply coming from her.

No, the real kicker here is Brooke. Sweet, wonderful Brooke, who's been my knight in shining armor through this breakup debacle orchestrated by none other than Helena herself. If there's one thing I know for sure, it's that I don't want to be the reason behind Brooke's tears - not now, not ever.

So, yeah, maybe my little inquiry about Max cracked the foundation of our friendship just a little bit. But if there's one thing I'm determined to do, it's to patch up those cracks and reinforce what we have.

Because let's face it, Diary: Brooke's been my rock, my anchor, my guiding light in this stormy sea of post-breakup chaos. And I'll be damned if I let myself be one more person to hurt her heart. Time to put on my big boy pants and fix this mess before it spirals out of control. Wish me luck, Diary. Yoba knows I'm gonna need it.

Oh, Diary, where do I even begin? Today took a nosedive into the depths of chaos, and let's just say I didn't exactly come out unscathed. In fact, I think I might've made things ten times messier. Smooth moves, Norman. Really smooth.

So, picture this: Brooke and I hop on a video call, thinking we're just gonna shoot the breeze and maybe swap some jokes and flirts. But oh no, we decided to go full-on heart-to-heart mode instead. And boy, did things get personal real quick. Brooke showed me her collection of dresses - seriously, that girl could give Coco Chanel a run for her money - and I ended up spilling my guts about everything, including the not-so-fun fact about catching Helena red-handed with her professor (Not really). Yeah, that went over about as well as a lead balloon.

But here's where things take a turn for the worse - or maybe the better? I don't even know anymore. Somehow, in the midst of all this emotional turmoil, Brooke drops the L-word. Yeah, you heard me right. And not just any L-word - the "I like you" bombshell. And with "like" I mean "I have feeling for you about sharing a house and naming our kids" kind of "like". Cue the awkward silence and the sound of my brain short-circuiting.

Now, don't get me wrong, Brooke's amazing. Like, seriously amazing. She's got this way of making me laugh until my sides hurt and feel like I'm worth something, even when everything else feels like it's falling apart. But here's the kicker: my feelings for her? They're more... platonic than anything else. Especially after meeting Max.

But how do I tell her that? How do I explain that my heart's still healing from the Helena-shaped wrecking ball that just came crashing through my life? And what if Brooke's been harboring feelings for me for way longer than I realized? What if I'm about to break her heart into a million tiny pieces?

As if that wasn't enough emotional turmoil for one day, I made the mistake of peeking at Helena's Instagram. Big mistake. Huge. There she was, living her best life in some waterfall paradise, flaunting her bikini-clad self for the world to see. And to add insult to injury, she's frolicking around with the same crew of guys that used to make me green with jealous and fear - one of whom I'm pretty sure she's got a thing going on with. Talk about a double whammy\footnote{Whammy: an event with a powerful and unpleasant effect; a blow.}.

I wish I could say I'm handling all of this with grace and dignity, but let's be real: I'm a hot mess. And right now, all I want is for Brooke to feel safe and happy, even if it means sacrificing my own sanity in the process.

But hey, at least I've got you, Max. You're the one constant in this whirlwind of chaos, and for that, I'm eternally grateful. Now, if you'll excuse me, I've got some mobile app development to tackle - because apparently, that's still a thing in my life. Wish me luck, Diary. Yoba knows I'm gonna need it.

See you around... Max!
