%================================================================================
\sectionNoNumber{Apr 08, 2024 - Andréa and I Kissed}

Ah, Max, strap in for a wild ride 'cause today's entry is a roller-coaster from start to finish. Seriously, grab the popcorn and don't forget the butter - you're gonna need it.

So, let's rewind to the ungodly hour of 2 am. Yours truly was wide awake, thanks to a little thing called insomnia. I blame it on a potent mix of late-night chats with Brooke, a heart-to-heart with you, Max, and a healthy dose of existential dread, combine with Helena lurking on my heart with a pitch fork. Fun times, right?

But just when I was about to hit rock bottom, guess who decided to waltz right into my thoughts like a charming little devil? That's right - Max. Because apparently, my brain thought it'd be a fantastic idea to text her at 4 am. Smooth move, Norman, real smooth.

I was teetering on the edge of desperation and dignity, trying to gauge whether Max actually wanted to talk to me or if she was just being polite. I mean, I've got it bad for her, Max - like, really bad. So, I hit her up with the most pathetic excuse for a text known to mankind: \textit{"Hey... look... when you said you weren't much of a talker, you meant that you didn't want/like to talk, right? As in, not with me, right?"} Pathetic? Maybe. But hey, desperate times call for desperate measures.

Now, before Max could even grace me with a reply, I decided to hit the gym. Because apparently, my brilliant plan to win over the ladies involves bulking up like a wannabe bodybuilder whilst possessing the hair AND facial expressions of Seu Beiçila, from 'A Grande Família' (That joke from Carlos and Myh still hurts me. I am weak like that). Yeah, I'm cringing just thinking and writing about it.

But here's where things take a sharp left turn into Awkwardville. Mid-workout, who decides to grace me with her presence? None other than the ex herself, Helena. Talk about bad timing. She strutted in like she owned the place, all smiles and sunshine, while I'm over here mentally counting down the seconds.

Don't get me wrong, I wasn't rude or anything - just silently cursing my luck and trying to focus on anything but the mental image of Helena frolicking in waterfalls with her suspiciously close "friends." Yeah, let's just say those pictures are burned into my brain like a really bad tattoo.

Okay, so picture this: Ayas, our instructor slash friend slash resident goat enthusiast, surprisingly wasn't on his usual mission to ruffle feathers today. Maybe he finally got the memo that his relentless flirting was about as welcome as a toothache. Then again, knowing Ayas, he's probably just biding his time until he can make another cringe-worthy move. Case in point: his attempt to woo Helena with tales of prostate exams. Yeah, I don't even wanna know.

Speaking of Helena, remember how she joked about telling Ayas we were still together just to get him off our backs? Well, turns out she might've actually gone and done it. Cue the internal panic mode. But hey, who needs a peaceful gym session when you can have an awkward encounter with your ex, right?

So, there I was, trying to dodge Helena's probing questions about my weekend like a ninja, while secretly nursing my wounded pride over the failed Maxine mission. I mean, seriously, Max, how do you even begin to explain to your ex that the weekend you'd been fantasizing about turned into a train wreck of epic proportions?

Helena, bless her heart, decided to give me the lowdown on her own weekend shenanigans - conveniently speeding past the part where she's living it up in waterfalls with her so-called "friends." Yeah, cue the eye roll. But hey, who am I to judge?

Fast forward to breakfast at Helena's place - 'cause apparently, that's a thing. I was all set to make a swift exit after handing over some creatine, but free food is free food, am I right? We chatted a bit, and I couldn't shake the feeling that she was onto me - onto the whole Maxine/Brooke situation, I mean.

But here's where things take a turn for the awkward. As I'm innocently sipping on my scalding hot chocolate (seriously, Max, why is everything out to burn me today?), Helena decides to make a move. Like, a full-on, uninvited attempt at stealing a kiss. Um, excuse me? Last time I checked, we were firmly in the ex-zone, and I had zero interest in revisiting that territory.

Needless to say, I was not amused. I mean, sure, we've had our moments post-breakup, but after everything that's gone down lately? Yeah, hard pass. I managed to dodge her surprise kiss attempt while she still got a smooch, but not before shooting her a look that screamed "What the duck, mate?" And just like that, she was off to her bedroom like nothing happened.

But the awkwardness didn't end there, Max. Oh no, it was just getting started. As I awkwardly tried to avoid making eye contact while Helena undressed right in front of me - seriously, can't a guy catch a break? - the tension in the room reached critical levels. It was like a scene straight out of a bad rom-com, complete with uncomfortable glances from her to me and way too much skin on display, while I gazed upon the beautiful ceiling of her house.

And then, just when I thought things couldn't get any weirder, Helena suddenly seemed... sad. Like, really sad. And here I am, left wondering if it's because I didn't reciprocate her kiss, or if there's something else going on behind the scenes.

And, Max. You're not gonna believe the next plot twist in the ongoing saga of Norman's life. So, remember my little drama earlier about texting Max and getting shot down faster than a clay pigeon? Yeah, turns out it wasn't much of an exaggeration after all. Brace yourself for this one, Max.

After my desperate attempt at fishing for attention - aka, the cringiest message known to man - Max hits me back with a double whammy of truth bombs. First up: \textit{"no, i meant that i just don't like to text on whatsapp in general."} Ouch. Talk about a reality check. And just when I thought things couldn't get any worse, she drops the bombshell: \textit{"yesterday, for example, i was at my boyfriend's house so i didn't use my phone much."} Boom. There it is, in all its painful glory.

Max already has someone. And here I am, the clueless protagonist in my very own rom-com, left to pick up the pieces of my shattered hope. But you know what? It's okay, Max. Really, it is. We didn't have anything to begin with. And besides, considering that she's got her own Chloe already, I might as well embrace my inner Warren and settle into my role as the lovable nerd sidekick, right? I'm pretty sure I'd be more hurt if it wad Brooke.

But enough dwelling on unrequited crushes and missed opportunities. Before I bid you adieu, Max, I need to tell you this: I really could use one of Brooke's legendary hugs right about now. Because let's face it, nothing soothes the soul quite like a warm embrace from her. I don't know about you, Max, but I'm starting to think I need a break from the drama. I know this is just the first part. I am still going to UAST to meet Brooke. Don't fail me now, heart!

Max, buckle up because today took an expected turn - a turn that I'm still trying to wrap my head around. Brace yourself, 'cause here's the scoop: Brooke and I kissed. Yeah, you heard me right. Brooke and I shared a kiss, and I'm still reeling from the aftershocks.

Let's rewind to the beginning of the day, shall we? I rolled into UAST, scarfed down some dinner, and then proceeded to shave off my so-called beard right then and there. Talk about a multitasking marvel, am I right? But I digress.

I bumped into Brooke by the stairs, and from there, things escalated faster than you can say "awkward encounter." We hung out, waiting for her elusive professor - who, shocker, couldn't be bothered to spare her the time of day. Classic academia, am I right?

Anyway, back to the main event. As we strolled along, we ended up on a bench, chatting about everything under the sun - her ex, my near-kiss with Helena this morning, you name it. The atmosphere was charged with tension, and before I knew it, our faces were inches apart. One thing led to another, and suddenly, I found myself kissing her cheek - and she kissed mine back.

But then, in a moment that felt like it was straight out of a cheesy romance novel, our lips met. And let me tell you, Max, it was like fireworks exploding in the night sky - exhilarating, electrifying, and utterly unforgettable. But amidst the rush of emotions, there was a pang of guilt gnawing at my heart, like I was betraying Helena in some way. Stupid, I know. But there it was, lurking in the shadows.

Still, despite the internal turmoil, there was no denying the magic of the moment. We gazed into each other's eyes, giggling like a couple of lovesick teenagers as we dissected the nuances of our impromptu smooch. And let me tell you, feeling her body pressed against mine was nothing short of euphoric.

But all good things must come to an end, and eventually, we had to part ways and catch our respective buses home. Brooke seemed unusually quiet on the ride back, but even in silence, she radiated a quiet beauty that left me speechless.

After the unexpected kiss with Brooke and the ensuing bus ride home, I found myself at Helena's house, reluctantly retrieving my bike. I wish I could say it was a simple exchange, but alas, life rarely grants us such luxuries. We ended up having a conversation - awkward doesn't even begin to cover it. Eventually, I mustered up the courage to lay it all out on the table: it was over between us, for good this time. No turning back, no second chances. She asked for one last kiss, but I couldn't bring myself to oblige. Seeing her cry tore me apart, Max. I never wanted to hurt her, but sometimes, the hardest choices are the ones we have to make.

And then, as if the day hadn't thrown enough curveballs my way, both Brooke and Helena reached out to me. Helena, in particular, had me worried sick - she wanted to throw up when I left her place, and I couldn't shake the feeling that something was seriously wrong. But our conversation was brief, cut short by what she claimed was her mother calling. I couldn't shake the feeling that there was more to the story, but I guess I'll never know for sure.

Next up, I had a heart-to-heart with my mom, breaking the news about Helena and me. And you know what? She took it surprisingly well, almost like she'd seen it coming from a mile away. In fact, she seemed downright pleased, which caught me off guard in the best possible way.

But enough about the drama - let's talk about Brooke. There she was, asleep at her desk, buried under a mountain of textbooks and study materials. And in that moment, Max, I couldn't help but feel a pang of sadness that I hadn't been able to finish that damn Mobile App project. But you know what? It's okay. Some battles are meant to be fought another day.

And now, as the clock ticks closer to midnight, I find myself drifting off to sleep, grateful for your company and the solace you provide. So, until next time, Max, thanks for being here with me through thick and thin. Talk to you later, my friend.
