\sectionNoNumber{Apr 19, 2024 - She admitted it}

This entry is being entered on May 5th. I couldn't enter it in the day, Max. I am sorry. You will know why soon enough, though.

On April 19th, 2024, which was a Friday, Helena, my ex, managed to twist her ankle or something, so we ended up agreeing on something else instead of gym. We had this plan to swing by her "garage" (aka her new eyebrow sanctuary) to catch up and, you know, tame these wild brows of mine. Once i got there, i was waiting for what felt like an eternity. And let me tell you, patience is not my strong suit.

Finally, when she rolls in, her mom goes all FBI on us, and we had to go into stealth mode. Like, ninja-level stealth, Max. We just didn't wanna deal with the whole lecture thing, you know?. It's not like we were plotting a heist or anything, we just wanted some quality hang time without getting lectured. Eventually, momma bear leaves us be, and it's eyebrow time.

Helena spills her guts about feeling all kinds of blue -- lonely, inadequate, you name it. I try my best to sprinkle some wisdom, but I'm not sure if I got through to her. After the brow magic, we settle in for a cozy breakfast sesh. Picture this: Helena perched on that door frame thing we used to share and sit on, and me, camped out on the floor like it's a picnic.

Now, here's where things take a turn. We dive into some  heart-to-heart conversation about Brooke and Professor Diego -- and yeah, Helena swears there's nothing going on there between the two of them. But as we chat, we're inching closer, like magnets drawn together. Before I know it, Helena was on my lap, locking eyes with me like it's the most natural thing in the world. And let me tell you, Max, that moment? That's one of those moments I wish I could just forget everything and make them last forever.

So there we were, deep in conversation, and Helena's rocking this tank top, right? And let me tell you, Max, it was hanging off her shoulders like it had a mind of its own. So, being the helpful friend I am, I lean in to fix her yoke, but she's all, "No. Don't put it back!" Next thing I know, my hands slip, and her breasts are out in the open.

Now, here's where things take a turn. Instead of freaking out, I'm just, like, drawn to them. So, yeah, I start giving 'em a little squeeze, and before I can even second-guess myself, Helena's all, "Kiss 'em." And, well, I'm not one to argue with a good suggestion, Max.

Let me tell you, it was like a rush of all the good feels you can imagine. And when I finally pull away, there she is, inches from my face, those eyes practically begging for more. It's like we're back in those early days, Max, when everything was fireworks and butterflies. And before I know it, our lips are locked.

So, there we are, catching our breath after those mind-blowing kisses, right? And then Helena drops this bombshell: "Quer dar uma entradinha?" Now, I know what you're thinking, Max, and believe me, I was thinking the same thing -- we shouldn't go there. We're not together anymore, and the drama surrounding us is enough to fill a soap opera. I told her we couldn't, but then she hits me with, "Mas você QUER entrar rapidinho?" And well, Max, I caved.

Now, here's the kicker -- I swear, I had no intention of taking things to that level. I just wanted to chat, maybe snuggle up a bit, you know? But somehow, we ended up in this tiny room, and Helena's asking if I brought the "thing." And of course, being the prepared gal that I am, I said yes. Spoiler alert: it wasn't a condom, Max, but a bottle of lube. Yeah, talk about awkward.

So, there we are, standing there, and next thing I know, we're broth drooping our paints just enough to expose that perfect ass of hers that I was always in love with. Nothing could compare. When I got inside her, it felt like one of the best feelings ever. Feeling her body pound mine while having her waist and hips in my hand was perfect. I truly wished that, at that moment, I could relive that moment forever. -- it was pure bliss, Max.

In that moment, I swear I could've stayed there forever. It was like all the stars aligned, and nothing else mattered but us. It felt like the best sex we ever had, Max, and believe me, I've got A LOT of memories to compare it to.

So, there we were, caught up in the heat of the moment, right? But deep down, I knew we had to pump the brakes. I told Helena we needed to stop, but she's all, "Go as fast as you can." And let me tell you, Max, it was like an adrenaline rush, taking things to a whole new level.

And then it happened -- I came, just like that. It was like a split-second decision, but in that moment, it felt like the only choice. And even after, I kept going, pounding away like there was no tomorrow. But eventually, reality hit, and we had to call it quits. Helena, she was beaming, Max. Like, I hadn't seen her that happy in ages.

But then, out of nowhere, it hits me -- this overwhelming sense of guilt, like a ton of bricks crashing down on me. I couldn't believe what I'd just done. I mean, Max, we didn't just kiss -- we went all the way. And as much as I tried to brush it off, the truth hit me like a freight train.

I felt like I had betrayed Brooke, like I had crossed a line I promised myself I wouldn't. My legs went weak, and I had to sit down. I've never felt regret like this before, Max. It's like a weight crushing my chest, suffocating me with every breath.

To be honest, Max, my head's spinning right now. It's like my mind's trapped in a fog, struggling to piece together what just went down. I remember blurting out to Helena that I needed to forget her, to move on, to be done with this mess once and for all. But then it happened -- I asked her about Diego, about whether they'd kissed. he hesitated for a split second. She said yes.

Turns out, they'd shared more than just a peck. She spilled the beans about them locking lips in some square with her crew, like it was no big deal. And get this -- it had been going on for a week, maybe even longer. It hit me like a ton of bricks, Max. The agony, the pain, the sheer disgust -- it was suffocating.

I couldn't hold it back, Max. I wanted to scream, to lash out, to tell her how much I despised her in that moment. I told her I came inside her and that she was taking the pill in that very morning.

I couldn't bear to look at her, Max. The sight of her made my skin crawl. So, I did the only thing I could think of -- I hopped on my bike, told her to take those damn pills, even if it was the last thing she ever did for me, shot her a look of pure disgust, and rode off under that cruel sun.

I didn't even make it to the gym, Max. I just headed straight home, drowning in a sea of anger, betrayal, regret, and heartache. It's like everything I thought I knew was ripped away from me in an instant, leaving me stranded in a world of pain.

You want a joke? Here's one for the books. Just two days earlier, on a seemingly innocent Wednesday, she swore up and down that there was nothing between her and Diego. No spark, no connection -- nada. Fast forward to today, and suddenly they've been swapping kisses for over a week. You know who was right all along? Her mom, Brooke, Carlos, even my own jealousy and overthinking. Talk about a punchline.

But wait, it gets even better. At one point, I mustered up the courage to ask her if any of this even phased her. The whole kissing Diego, breaking my heart into a million pieces, lying through her teeth -- did she regret anything? You'll never believe what she said. Brace yourself -- she actually regretted telling me about her and Diego. Yeah, that's it. That's her big regret. Not the pain she caused, not the trust she shattered -- just that I now know the truth. Comedy gold, right?

Max, this is where the day takes a turn, but thankfully, there's a glimmer of light at the end of the tunnel. So, picture this -- I'm feeling like absolute garbage all day long. I had to drag myself to college, sit through an Infra class, the whole nine yards. And let me tell you, Max, it was like dragging myself through quicksand.

But then, after class, I bump into Brooke and her squad in front of "Bloco 02." And honestly, Max, I don't remember much after that. I was there, but my mind was a million miles away.

Once I finally made it home, Brooke and I hopped on a video call. And let me tell you, Max, it was like she could sense something was off. She straight-up asked if I was okay, and try as I might, I couldn't keep it in. I spilled the beans about my little rendezvous with Helena that morning -- well, most of it, at least.

I told her about our plans to hang out, do my eyebrows, all that jazz. And yeah, I fessed up about the kiss, but I couldn't bring myself to tell her about the other stuff. It's like, deep down, I knew it would crush her, Max. But here's the thing -- just opening up to her, hearing her soothing words, it was like a balm to my wounded heart. She knew exactly what to say, Max, like she had this magic touch that could chase away all the darkness.

And in that moment, Max, I wanted nothing more than to reach through the screen and kiss her senseless. I mean, I'm beyond lucky to have her in my corner, Max. She's my rock, my safe haven in a storm of chaos. But here's the kicker -- as Brooke drifted off to sleep, I found myself at peace, thanks to her. It's like her presence alone was enough to chase away all the demons (and the exes) haunting me. And for that, Max, I'll forever be grateful.
