\sectionNoNumber{Apr 09, 2024 - Helena and Her Knight}

Hey there, Max. Brace yourself, 'cause today's entry comes with a big ol' dose of self-loathing. Here goes nothing.

So, Helena had a rough night -- like, hospital-worthy rough. And you know what? I wanted to be there for her, to lend a helping hand and all that jazz. But in the end, I chickened out. I know, I know – I'm a real piece of work.

Instead, she called up Diego – yeah, the same Diego I used to be jealous of – and he swooped in like a knight in shining armor, whisking her off to the hospital in his fancy car. Talk about a punch in the gut.

Fast forward to today, and I find myself paying Helena a visit to check up on her. And let me tell you, Max, what I saw when I walked through that door knocked the wind right out of me. She wasn't wearing anything on her chest, and suddenly, the world felt like it was tilting on its axis.

But here's the kicker, Max: Helena has feelings for Diego. Romantic feelings. And you know what's even worse? I'm pretty damn sure he feels the same way about her. Cue the existential crisis.

When Helena spilled the beans about calling Diego and him rushing to her side like some kind of hero, it felt like a dagger to the heart. And then she dropped the bombshell about seeing the picture of me and Brooke – holding hands, no less – and let me tell you, Max, the guilt hit me like a ton of bricks.

But here's where things take a turn for the downright disastrous: while lying there with Helena, something snapped. Something stupid and reckless and unforgivable. We kissed. And now? Now I'm stuck in this never-ending cycle of self-loathing, wondering why the hell I did something so monumentally stupid.

I wish I could tell you more, Max – spill all the gory details and get it off my chest. But alas, duty calls, and I've got a date with destiny – or rather, a date with Brooke. She's the only one here for me now, and I can't help but feel a pang of relief at the thought of escaping this mess, if only for a little while.

But before I sign off, there's one last thing I need to tell you: I made Helena a promise. "Saturday. 4pm. Here," I said. And you know what? She replied with "bring the thing." But between you and me, Max, it's an empty promise – a feeble attempt to ease the ache in my chest.

I'm sorry, Max. I'll catch up with you later. Until then, wish me luck – I'm gonna need it.

%================================================================================
