\sectionNoNumber{Jan 28, 2026 - Afonso’s Birthday}

Okay, Max.

This is gonna be one of those days. You know the type. The kind where everything happens before sunrise and I could dedicate an entire chapter for it if I cram two more entries like this together. So yeah. Brace yourself.

\subsectionNoNumber{06:00 - Going to Petrolândia}

I woke up at, like, 3 a.m. Which is not a real time. That’s night pretending to be morning. Immediately awful.

I had to take this van that costs around 60 bucks, because Junior decided to come with us—and he kinda can’t travel alone. Also, he was paying for Afonso’s ticket, and honestly it would’ve sucked to make him take the more expensive van and still pay for Afonso. Anyway. Decisions were made.

Also: I was NOT ready. At all.
No luggage.
No clothes picked.
Hair? Untouched.
Plans? Zero.
Food? Not even coffee. Not even bread. Absolutely nothing. Past Me really said “future me can deal with it” and vanished, LMAO.

So there I was, speed-running my entire existence at 4 a.m., trying to look like a functional human being.

Thank God my mom was there. And by “there,” I mean: not actually helping, lowkey judging my outfit choices, and talking way too much—but she lent me 50 bucks, which honestly saved my life. Financial support > emotional support at this hour.

Eventually I got (kind of) ready. I called the van guy and he was like, “I'mma pick you up right now.”
Max, I was not ready.
He gave me 20 minutes. A blessing. A second chance at life.

Everything was fine.
Until we got inside the damn van.

That thing was CRAMMED. It wasn't a sardine, like campus', but still. Some people were literally traveling standing up. The air was warm and thick and hard to breathe, like the van itself was tired of existing. For the first time in years, I actually got nausea while traveling.

At some point, I just stared into nothing and told myself—like, three times: “Don’t be a weak bitch. You’re fine.”

And somehow… I was fine.
Which is weird and I would never let myself treat anyone like that... not after so many people have done that to me when I was little. Weird to think that, now, I do that to myself.

But yeah. Brain said “nah” to passing out, and we moved on.

And that was just 06:00.

\subsectionNoNumber{09:00 - I Love Sunny’s Family}

So around 9 a.m. I finally arrived in Petrolândia. Finally.

The driver took this very specific turn to drop another passenger right at their doorstep. When it was my turn to take an almost identical turn so I could be dropped at my destination, the driver basically said: “Nah.”

And just left me on the main highway.
Cool. Love that for me.

I thought I only had 55 bucks left. Turns out I actually had 65, and he took his 60. So there I was, dragging two heavy bags plus a sad plastic bag, walking all the way to Sunny’s house like I was on a low-budget coming-of-age movie montage.

But.
Important detail: I stopped to buy ice cream first.
Because I was STARVING for something sweet, Max. Like, emotionally and physically. Survival instincts kicked in and they said “sugar, now.”

When I finally got to Sol’s house—Sol being Sunny’s mom, who I call Tia like it’s the most natural thing in the world—she saw me and immediately went in for a hug. Instant warmth. She opened the huge sliding door (we met at her store first) and welcomed me in like I belonged there.

Inside were Afonso (the birthday boy, the reason for all this chaos) and Doid (Junior) already hanging out. Sunny and Aisha—aka Minhoca—were there too. I hugged everyone. Full hug circuit completed.

And honestly?
The very first thought that hit me after hugging Tia and Minhoca was:
I FUCKING LOVE SUNNY’S FAMILY.

Like—especially that tiny stick of a human with the googly eyes and the cutest smile ever. Max, I’m not exaggerating: Aisha might be the cutest fucking thing I’ve ever seen in my life. It should be illegal to be that adorable.

Also, side note (important): I love how Aisha treats me like I’m her favorite person.
Afonso interacts with her like the brother-in-law he is.
Junior plays with her a lot.
They both treat her like a kid, doing pretend stuff, touching and hugging her and all that.

But me?
I just treat her like a person. I talk with her. Joke with her. I ask her opinions and permissions. Respect her in a way. I don't force stuff or play games. Yet, she always talks to me. 

She always asks me stuff and she always invites ME for activities. She could be being hugged by Afonso and playing with Junior, and she still would get out of there, pluck my shirt and say "Hey, Vinni. Wanna draw with me?" and we would draw and talk like two close friends. She would even ignore the other and invite me on a chocolate heist with her. Dam, I love this. 

Also, We NEVER touch. Like, ever. That's something I love too, because I hate touching and she never goes to touch Afonso or Junior. So, we only hug to say hi or bye, and that's it. If she NEED a hug or a "pick me up", I'd just brush her off and tell her to go after someone else lmao.

Sometimes it's like she’s my sister.
Which is funny, because she’s nothing like Bea—my actual sister—who is way saltier and way more of a smart-ass.

God, I miss my salty smart-ass sister.

And now I need to give Bea a new nickname, because I gave Jainy the same one, and my brain refuses to separate them. Which is annoying. And confusing. And emotionally inconvenient.

Anyway.
Sunny’s family = elite.
My heart = already soft.
And it’s still morning.

\subsectionNoNumber{10h22 - Sunny's Tarot Cards}

\subsectionNoNumber{11h00 - Painting with Aisha}

At 12h11, Aisha and I finished our drawings
