%================================================================================
\partNoNumber{THE BEGINNING}\markboth{}{}
%================================================================================
\sectionNoNumber{Hello there!}

Okay... Howdy! So this is happening. Hi, journal. Or diaries. Or... thing that will know way too much about me. I gotta remember to give you a name.

\sectionNoNumber{I'm Norman.}

My name is Norman Vinícius P. Santos (Please, call me just Norman... or Nih), I have amnesia and, after a certain inspiration, the idea of keeping my memories in paper (or pixels) came to be. If you’re reading this, congratulations—you’re officially my emotional storage unit! 

\sectionNoNumber{The Many Many Diaries.}

This one is called Norman’s Diaries, which is not one diary, but a collection of them, because apparently one notebook isn’t enough to hold an entire human being (rude, honestly).

Think of this as a time capsule, except messier, louder, and full of bad jokes, random thoughts, unfinished feelings, and moments that felt huge for exactly five minutes. Or five years.

This journal contains: 

Diary of 2002 to 2023: The years that I didn't had any journal.

Diary of 2024: The craziest year of my life.

Diary of 2025: The roller-coaster year.

Diary of 2026: The one in which I'm remaking my journals

And More Diaries. And this is how it works.

Every year gets its own diary. Like its own little universe.
I’m writing this text right here in January 26th, 2026, which means: hi, present me!
But you might stumble into diaries from years I haven’t even mentioned yet. Surprise! Time travel is real.

If you’re confused, don’t worry—that probably means I was confused too.
Different years, different versions of me. Same handwriting. Same brain.
Hopefully a little more wisdom… but no promises

\sectionNoNumber{The Chapters of My Life}

So yeah, each diary is also split into chapters, because my life apparently works in seasons.
Each chapter lasts about a month-ish and gets named after whatever took over my brain during that time.

People. Events. Feelings. Random chaos.

For example: when I met my close friends and we created the Tabacudos group, that became... everything.
So that chapter of my life is literally called “Tabacudos”.
Simple. Honest. Very me.

Before each chapter starts, I’ll try (keyword: try) to write a small intro explaining what was happening and why that name made sense at the time.
Future-me, if you’re reading this and thinking “wow, that name was dramatic”… yeah. I know.

Now, about the entries themselves—there’s not much to explain, really.

Each day gets one entry.
No more, no less. Rules! Look at me being organized as always.
Inside that day, I can break things into little sections if my thoughts start multiplying like gremlins.

Every entry starts with: the date and a clever title (or at least something I thought was clever at the time)

And the content is... well...

Some days I’ll write about important life stuff.
Some days I’ll write about absolutely nothing and somehow make it dramatic.
Some days I’ll overthink one sentence someone said to me three years ago like it just happened five minutes ago.
Some days I’ll complain, joke, romanticize my sadness, or pretend I’m the main character in an indie game where everything means something.

Basically, diary…
This is where my life goes to be processed.

\sectionNoNumber{My Inspiration}

And yeah—this is inspired by Maxine Caulfield.

She kinda proved that journaling doesn’t have to be boring, serious, or “Dear Diary, today I learned a valuable lesson

It can be messy.

It can be honest.

It can be funny, emotional, and slightly embarrassing.

It can contradict itself

It can change its mind mid-sentence.

It can literally talk back to you.

And that’s the version of journaling I want.
Not perfect.
Just… real.

\sectionNoNumber{Your Name is...}

So, since I’m clearly talking to *you*, I should probably give you a name.

Your name is Max.

Yeah, I know. On the nose. But it feels right.

You, Max, are the one listening right now—whether you’re the journal itself, or some future version of me, or someone who accidentally opened this and decided to keep reading.
No pressure or anything.

So, Max… expect conversations.
Expect rambling.
Expect random side notes like “why did I write that??” and “okay, that was dramatic.”

This isn’t about being cool.
This isn’t about sounding smart.
This is about being real.

If I ever stop writing here, I hope it’s because I was out there living something good—something worth remembering.
Something so strong that even my fucked up amnesia won’t be able to erase it.

And if I keep writing...
Well, then I guess this worked.
And I needed it.

%============================================================--------------------
\sectionNoNumber{Final Notes (aka the cheesy outro)}

If you’re reading this — thanks for being here. 

Whether you’re my future self, some random stranger, or a curious alien trying to understand human life (in which case, howdy!) — I hope this gives you a glimpse into what it means to be me. (SPOILER: I suck. :v)

%--------------------------------------------------------------------------------

