%================================================================================
\partNoNumber{THE END}\markboth{}{}

Okay... 

If this is the end of this journal, then wow. We actually made it here.

If I’m reading this at the end of everything, then this page is proof that I was here. That I felt things. That I cared. That I tried. 

And I'm sorry to say this, but it also means I probably died and stopped writing it. Either that or I just stopped writing for other reasons hahaha. 

You’ve seen all my eras:

the confused ones,

the hopeful ones,

the heartbroken ones,

the “I swear I’m fine” ones (I was not fine).

You’ve held my thoughts when they didn’t make sense yet.

You’ve kept secrets I didn’t even know how to say out loud.

You’ve watched me grow without judging, interrupting, or telling me to “just move on”.

If future-me is reading this:
Hey. You survived more than you thought you would.

I hope you’re gentler with yourself now.

I hope you still feel deeply.

I hope you still notice small things.

I hope you still write—somewhere, somehow—even if it’s not here.

And if this journal ends because life got louder, happier, fuller... then that’s okay too.
That just means the story kept going off the page.

So yeah.
Thank you for being my witness.
For holding versions of me that no longer exist.
For reminding me that moments matter—even the quiet ones.

I hope this isn’t really goodbye. That it’s just a pause.

Whatever it is, I hope to see you some day.

Take care. I love you!

\quad

"Norman was here!"
