%================================================================================
\partNoNumber{Quotes}

%--------------------------------------------------------------------------------

"Writing a journal is the start of something new and slightly terrifying. I mean, giving life to a journal feels like I’m conjuring some sort of magical creature." \\
- Norman Whittlecliff, April 7th, 2024

\quad

"For future me — or anyone else reading this — you might be in a tough spot right now. If you are, I need you to remember something. Remember the storm that was the start of 2024. It was brutal, but it led to the brightest, most beautiful year of my life. Things will get better. They always do. Keep smiling. Keep laughing. Keep moving forward."\\
- Norman Whittlecliff, January 1st, 2025

\quad

"I like to think that I died... and that god sent me back to earth to enjoy my life a little more. To smell flowers again. To walk under the rain. To laugh again until I can't breathe. To taste food I was too stubborn to eat before. To fall in love again. To live." \\
- Norman Whittlecliff, January 1st, 2024

\quad


"I thought I had to keep moving forward after losing Maka for good. But here I am, a walking disaster making one bad choice after another. I’m a mess, Max. Like, certified stupid boy vibes." \\
- Norman Whittlecliff, January 9th, 2024

\quad

"You’re my constant, Max. The glue holding this beautifully chaotic journal together. You’re more than a diary: You are my life on paper. The one I can count and tell everything. I might even get your name tattooed someday. Can you imagine? Me, walking around with “Max” inked on my skin like a badge of honor. That’s how much you mean to me." \\
- Norman Whittlecliff, January 11th, 2025

\quad

"Where one doesn’t want to, two ain’t getting it done."\\
- Norman Whittlecliff, January 15th, 2025

\quad

"Some people might vanish. Others might stay forever. Either way, if they made it into this journal of mine, it means they mattered. Even just for a moment. And that’s worth writing down." \\
- Norman Whittlecliff

\quad

"As we grow into different people, she’ll see me as nothing more than a mistake, a phase. And me? I’ll still love her." \\
- Norman Whittlecliff, March 11th, 2025

\quad

"I'll be unreasonably delusional about what I want until it's my reality." \\
- Norman Whittleclif, April 07, 2025

\quad

"I feel like I’m watching someone drown while telling me they love the water." \\
- Norman Whittlecliff, May 7th, 2025.

\quad

"I don’t stay with her because I can — I stay because I want to. And that’s love, isn’t it? Wanting. Choosing. Over and over again." \\
- Norman Whittlecliff, September 19th, 2025.

\quad

"He’s scared of love now because he can love, and knows it’ll hurt. I don’t even bother with love because I can’t love the way I used to. Deep, right? Yeah, we’re philosophers now, apparently." \\
- Norman Whittlecliff, September 22th, 2025.

\quad

"Like… is this what being in a relationship is supposed to feel like? Just pain with sprinkles and occasional sex for play-pretend?" \\
- Norman Whittlecliff, September 26th, 2025.

\quad

"So yeah. I guess all I can do is wait and see which future happens. If I am going to choose loneliness over disrespect… Then I need to be strong, Max. Really strong." \\
- Norman Whittlecliff, September 26th, 2025.

\quad

"I didn’t lose her. She lost me. And somehow I’m still the one bleeding, like I'm about to die." \\
- Norman Whittlecliff, January 6th, 2026.

\quad

"They say the third big love is supposed to be forever. Maybe that's meant for the memories and the pain, not the companionship itself." \\
- Norman Whittlecliff, January 6th, 2026.

%--------------------------------------------------------------------------------

\quad

"(Vini,) Vc está muito feliz sem aquela garota. É nítido." \\
- Isabella Manhez, April 07, 2025

\quad

"Eu tava de boa na aula. Do nada uma mensagem do meu amigo dizendo que o Gojo tava na UAST. Ai eu desci e vi tu. Eu eu pensei 'Eu tenho que ser amigo desse retardado' e ai foi isso." \\
- Iraci (Não-convidada)

\quad

"A gente cura os traumas com comédia." \\
- Iraci (Não-convidada), August 14, 2025

\quad

"Eita suco bestaferamente gelado." \\
- Iraci (Não-convidada), September 12, 2025

\quad

"Não existe dependência sem amor tlgd? Mas existe amor sem dependência" \\
- Andrey Estima, November 2, 2025

%--------------------------------------------------------------------------------

"Keep moving forward. Even if you die. Even After you die." \\
- Ehren Yeager (Attack on Titan)

\quad

"No half measures!" \\
- Mike Ehrmantraut (Breaking Bad)

%--------------------------------------------------------------------------------

Caso amanhã eu não esteja aqui, eu quero que cada sorriso que um dia eu tirei de você te faça levar um pedacinho da minha eternidade ensse plano perto de você. Porque caso amanhã eu não esteja aqui, quero que o tempo não apague o amor que um dia foi recíproco. Porque, caso amanhã eu não esteja aqui, eu quero que você saiba que você foi a minha maior certeza em um mundo que só me apresentou dúvidas. Caso amanhã eu não esteja aqui, saiba que o meu espírito estará te protegendo e te guardando. Porque caso amnhã eu não esteja aqui, eu quero que você saiba que cada abraço que eu te dei era a minha maneira de dizer que você sempre foi o meu porto seguro. Caso amanhã eu não esteja aqui, eu quero que você saiba que cada estrela que tem no céu contém os sonhos e alegrías que eu desejo pra você. Basta só você olhar para o céu porque, caso amanhã eu não esteja aqui, você vai estar em mim pra todo sempre.
